\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-01-23 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a description of how to check the quality of a mesh generated using our in-house mesher

Prior to running and compiling this code, you have to export your mesh in CUBIT to an ABAQUS (.inp) format.
You also have to determine a number of parameters of your mesh, such as the number of nodes and number of elements
and modify the header of the \texttt{check\_mesh\_quality\_CUBIT\_Abaqus.f90} source file. Then,
in the directory \texttt{src/check\_mesh\_quality\_CUBIT\_Abaqus}, type
\begin{lyxcode}
{\small ./compile\_all.csh}{\small \par}
\end{lyxcode}
and use
\begin{lyxcode}
{\small xcheck\_mesh\_quality\_CUBIT\_Abaqus}{\small \par}
\end{lyxcode}
to generate an AVS output file (\texttt{\small AVS\_meshquality.inp}
in AVS UCD format) or OpenDX output file (\texttt{\small DX\_meshquality.}~\\
\texttt{\small dx}) that can be used to investigate mesh quality,
e.g, skewness of elements and a Gnuplot histogram (\texttt{\small mesh\_quality\_}~\\
\texttt{\small histogram.txt}) that can be plotted with gnuplot (type
`\texttt{\small gnuplot plot\_mesh\_quality\_histogram.gnu}'). The
histogram is also printed to the screen. If you want to start designing
your own meshes, this tool is useful for viewing your creations. You
are striving for meshes with elements with `cube-like' dimensions,
e.g., the mesh should contain no very elongated or skewed elements.

@@

>>>>

Prior to running and compiling this code, you have to export your mesh in CUBIT to an ABAQUS (.inp) format.
You also have to determine a number of parameters of your mesh, such as the number of nodes and number of elements
and modify the header of the \texttt{check\_mesh\_quality\_CUBIT\_Abaqus.f90} source file. Then,
in the directory \texttt{src/check\_mesh\_quality\_CUBIT\_Abaqus}, type
\begin{lyxcode}
{\small ./compile\_all.csh}{\small \par}
\end{lyxcode}
and use
\begin{lyxcode}
{\small xcheck\_mesh\_quality\_CUBIT\_Abaqus}{\small \par}
\end{lyxcode}
to generate an AVS output file (\texttt{\small AVS\_meshquality.inp}
in AVS UCD format) or OpenDX output file (\texttt{\small DX\_meshquality.}~\\
\texttt{\small dx}) that can be used to investigate mesh quality,
e.g, skewness of elements and a Gnuplot histogram (\texttt{\small mesh\_quality\_}~\\
\texttt{\small histogram.txt}) that can be plotted with gnuplot (type
`\texttt{\small gnuplot plot\_mesh\_quality\_histogram.gnu}'). The
histogram is also printed to the screen.
Analyze that skewness histogram of mesh elements to make sure no element has a skewness above approximately 0.75, otherwise the mesh is of poor quality (and if even a single element has a skewness value above 0.80, then you must definitely improve the mesh).
If you want to start designing
your own meshes, this tool is useful for viewing your creations. You
are striving for meshes with elements with `cube-like' dimensions,
e.g., the mesh should contain no very elongated or skewed elements.

@@

To control the quality of the mesh, check the standard output (either on the screen or in the \texttt{in\_out\_files/OUTPUT\_FILES} directory in \texttt{output\_mesher.txt}) and analyze the skewness histogram of mesh elements to make sure no element has a skewness above approximately 0.75, otherwise the mesh is of poor quality (and if even a single element has a skewness value above 0.80, then you must definitely improve the mesh). To draw the skewness histogram on the screen, type \texttt{gnuplot plot\_mesh\_quality\_histogram.gnu}.
